Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-04-22 manuscript.tex
convert to ieee journal

%% 
%% Copyright 2007-2025 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.3 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

% \documentclass[preprint,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
% \documentclass[final,3p,times,authoryear]{elsarticle}
% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
% \documentclass[final,5p,times,authoryear]{elsarticle}
\documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

% \usepackage{balance}
\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{template}
\input{\template/preamble/preamble_Elsevier.tex}

@@

% %% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
% %% The amsmath package provides various useful equation environments.
% \usepackage{amsmath}
% %% The amsthm package provides extended theorem environments
% %% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Nuclear Physics B}

@@

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

@@

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author{
  Myeongseok Ryu, Donghwa Hong, and Kyunghwan Choi
} %% Author name

%% Author affiliation
\affiliation{organization={
  Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST)
},%Department and Organization
            addressline={123 Cheomdangwagi-ro, Buk-gu}, 
            city={Gwangju},
            postcode={61005}, 
            % state={},
            country={Korea}}

@@

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Research highlight 1
\item Research highlight 2
\end{highlights}

%% Keywords
\begin{keyword}
Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep input constraint

%% keywords here, in the form: keyword \sep keyword
%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% Add \usepackage{lineno} before \begin{document} and uncomment 
%% following line to enable line numbers
%% \linenumbers

%% main text
%%

@@

Many engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.

@@

Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
he following section will provide a detailed review of the existing solutions to these challenges.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
    \label{fig:ctrl:diagram}
\end{figure}

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{6.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
    \hline
    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
    \hline
    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
    \hline
    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

@@

%% If you have bib database file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-harv} 
\bibliography{\template/refs}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

%% Refer following link for more details about bibliography and citations.
%% https://en.wikibooks.org/wiki/LaTeX/Bibliography_Management

% \bibliographystyle{elsarticle-harv}
% % \bibliography{}
% \bibliography{\template/refs}

@@

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

>>>>

\documentclass[lettersize,journal]{IEEEtran}

\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{template}
\input{\template/preamble/preamble_journal.tex}

@@

\addbibresource{\template/refs.bib}

@@

@@

\author{
  Myeongseok Ryu, Donghwa Hong, and Kyunghwan Choi
\thanks{
    Myeongseok Ryu, Donghwa Hong and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: \{dding\_98, ???, khchoi\}@gist.ac.kr).

    This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No. KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (RS-2025- 00554087). (Corresponding author: Kyunghwan Choi)
    }}

\markboth{Journal of \LaTeX\ Class Files,~Vol.~18, No.~9, September~2020}%
{How to Use the IEEEtran \LaTeX \ Templates}

\maketitle

@@

\begin{IEEEkeywords}
    Neuro-adaptive control, constrained optimization, deep neural network, input constraint.
\end{IEEEkeywords}

@@

\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.

@@

Therefore, addressing these two key issues—eensuring weight boundedness and satisfying input constraints—is essential for th reliable design of neuro-adaptive controllers. 
he following section will provide a detailed review of the existing solutions to these challenges.

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=.69\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
    \label{fig:ctrl:diagram}
\end{figure*}

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{9.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
    \hline
    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
    \hline
    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
    \hline
    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

@@

\printbibliography

% \begin{IEEEbiographynophoto}{Jane Doe}
%     Biography text here without a photo.
% \end{IEEEbiographynophoto}

\begin{IEEEbiography}[{
    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/msRyu.jpg}}]{IEEE Publications Technology Team}
    In this paragraph you can place your educational, professional background and research and other interests.
\end{IEEEbiography}

\begin{IEEEbiography}[{
    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/dhHong.jpg}}]{IEEE Publications Technology Team}
    In this paragraph you can place your educational, professional background and research and other interests.
\end{IEEEbiography}

\begin{IEEEbiography}[{
    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/khChoi.jpg}}]{IEEE Publications Technology Team}
    In this paragraph you can place your educational, professional background and research and other interests.
\end{IEEEbiography}

@@
